---
title: "Leukemia"
output: ioslides_presentation
author: Emma Ahrensbach Rørbeck (s173733), Julie Maria Johansen (s174595), Simone Majken Stegenborg-Grathwohl (s174596) and Charlotte Würtzen (s174564)
--- 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("tidyverse")
load(file = "../data/_raw/golub.RData")
```


## Introduction

- Leukemia data set
- why interesting

# Methods

## Data wrangling
- Tidyverse
- pluck x and y from golub data and make into tibbles
- bind_cols

```{r, echo = TRUE}
x_data <- golub %>% 
  pluck("x") %>% 
  as_tibble()
```

- show snip of data before pivot_longer
- main functions: pivot_longer, mutate
- add id and type

## Modelling

- logistic regression => statistics (~tidy function)
- finding significant genes

- PCA
- K-means


# Results 

## histogram
## heatmap
## bar plot
## boxplot
## (scatterplot)


# Discussion

- important to distinguish which genes are important/significant
- missing reference/control group to compare with healthy individuals
- data set possibly more suitable for neural network analysis => prediction of cancer type
- PCA and K-means not relevant for this data? 
dimensionality reduction not ideal when variance explained is so low for each PC
Not clear cluster differentiation

## Conclusion

- sum up




